Nail: A practical interface generator for binary formats

### 2014-04-01 paper/design.tex
consistent footnote spacing

The many combinator also works on constant parsers, although as described above it can make the
generator not bijective. \footnote{By default, the generator will emit exactly one iteration of the
  constant parser in its output.} Example: \texttt{many uint8= "test"}

>>>>

The many combinator also works on constant parsers, although as described above it can make the
generator not bijective.\footnote{By default, the generator will emit exactly one iteration of the
  constant parser in its output.} Example: \texttt{many uint8= "test"}

### 2014-04-01 paper/intro.tex
consistent footnote spacing

A look at the CVE database or Hacker journal such as \textit{Phrack} shows that such design patterns
and the security problems they cause are rampant. Input processing libraries such as libpng
\footnote{\url{http://www.cvedetails.com/vulnerability-list/vendor_id-7294/Libpng.html} shows 24
remote exploits in the between 2007 and 2013.} or Adobe's PDF and Flash viewers are notoriously
plagued with input bugs. Even simpler formats such as the \textit{zlib} compression library have
historically contained multiple security
flaws\footnote{\url{http://www.cvedetails.com/vulnerability-list/vendor_id-72/product_id-1820/GNU-Zlib.html}}.

@@

Unfortunately, grammars are seldom used directly to recognise machine-created input. For example,
the security-critical and very well-engineered MIT Kerberos distribution uses parser
generators, but only for handling configuration files. A notable exception is the Mongrel
web server \footnote{\url{http://mongrel2.org/}} which uses a grammar for HTTP written in the
Ragel~\cite{ragel-paper} regular expression language. Mongrel was re-written from scratch multiple
times to achieve better scaleability and design, yet the grammar could be  re-used across all iterations~\cite{patterson-citation}.

@@

\subsection{Motivation}
\paragraph{Motivation}
While it is possible to express short transformations on the input entirely as semantic actions
\footnote{This is in fact the design rationale, to perform computation on the fly as the parser
  walks the parse tree.}, more complicated programs usually construct an internal representation,
which contains all relevant information from the input in a format native to the programming
language used. For example, a C programmer ideally wants to deal with structs and NULL-terminated
arrays, whereas a C++ programmer might expect STL containers, a Java programmer interfaces, a
Haskell programmer records and a LISP programmer property lists. 
 The structure of this internal representation usually resembles the structure of the grammar.

@@

A similar problem occurs when the programmer wants to generate output. 
Even though not all programs may use the same format for output as they do on input, different
programs might use the same format for input and output and re-using the same grammar is a good way
to save engineering effort and reduce parser differentials.
Some parser generators, e.g.
Boost.Spirit \footnote{\url{http://www.boost.org/doc/libs/1_55_0/libs/spirit/doc/html/index.html}},
allow the same grammar to be re-used for generating output from the intermediate representation.
However, those generators require a new set of semantic actions to be written, even though the
relationship between grammar and intermediate model was already expressed in the actions for the
parser.

>>>>

A look at the CVE database or Hacker journal such as \textit{Phrack} shows that such design patterns
and the security problems they cause are rampant. Input processing libraries such as libpng\footnote{\url{http://www.cvedetails.com/vulnerability-list/vendor_id-7294/Libpng.html} shows 24
remote exploits in the between 2007 and 2013.} or Adobe's PDF and Flash viewers are notoriously
plagued with input bugs. Even simpler formats such as the \textit{zlib} compression library have
historically contained multiple security
flaws\footnote{\url{http://www.cvedetails.com/vulnerability-list/vendor_id-72/product_id-1820/GNU-Zlib.html}}.

@@

Unfortunately, grammars are seldom used directly to recognise machine-created input. For example,
the security-critical and very well-engineered MIT Kerberos distribution uses parser
generators, but only for handling configuration files. A notable exception is the Mongrel
web server\footnote{\url{http://mongrel2.org/}} which uses a grammar for HTTP written in the
Ragel~\cite{ragel-paper} regular expression language. Mongrel was re-written from scratch multiple
times to achieve better scaleability and design, yet the grammar could be  re-used across all iterations~\cite{patterson-citation}.

@@

\subsection{Motivation}
\paragraph{Motivation}
While it is possible to express short transformations on the input entirely as semantic actions\footnote{This is in fact the design rationale, to perform computation on the fly as the parser
  walks the parse tree.}, more complicated programs usually construct an internal representation,
which contains all relevant information from the input in a format native to the programming
language used. For example, a C programmer ideally wants to deal with structs and NULL-terminated
arrays, whereas a C++ programmer might expect STL containers, a Java programmer interfaces, a
Haskell programmer records and a LISP programmer property lists. 
 The structure of this internal representation usually resembles the structure of the grammar.

@@

A similar problem occurs when the programmer wants to generate output. 
Even though not all programs may use the same format for output as they do on input, different
programs might use the same format for input and output and re-using the same grammar is a good way
to save engineering effort and reduce parser differentials.
Some parser generators, e.g.
Boost.Spirit,\footnote{\url{http://www.boost.org/doc/libs/1_55_0/libs/spirit/doc/html/index.html}}
allow the same grammar to be re-used for generating output from the intermediate representation.
However, those generators require a new set of semantic actions to be written, even though the
relationship between grammar and intermediate model was already expressed in the actions for the
parser.
